Supplementary material

### 2014-07-31 manuscripts/supplement.Rmd
supplement updated using newer phytools to plot sparql cladogram

```{r}
newick <- paste(recurse(root), ";", sep = "", collapse = "")
tree <- read.newick(text = newick)
collapsed <- collapse.singles(tree)
plot(collapsed, type = "cladogram")
```

>>>>

```{r}
newick <- paste(recurse(root), ";", sep = "", collapse = "")
tree <- read.newick(text = newick)
collapsed <- collapse.singles(tree)
plot(collapsed, 
     type='cladogram', 
     show.tip.label=FALSE, 
     show.node.label=TRUE, 
     cex=0.75, 
     edge.color='grey60', 
     label.offset=-9)
```
